---
title: "Diary of Anne Frank Project"
author: "Jeffrey Easterling"
date: "2024-02-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### The Diary of Anne Frank is a well-known work made readily available to the 
### public. Apart from its popularity and reputation, a number of its other features
### warrant examination: its relative brevity and iterative format lend it to within
### text comparison between entries. Furthermore, this particular edition at least
### third revision of the text. The original A written by Anne, the B edited by
### her father, Otto, and this particular edition, C, by Mirjam Pressler who 
### reintroduced and edited passages from A.

### Set working environment

```{r}
getwd()
setwd("~/Projects/POLS5773/CEU_text_analysis/coding_practice/diary_annefrank")
```

### Required Packages

```{r, message=FALSE, results='hide'}
library(tm)
library(tidyverse)
library(ggthemes)
library(ggrepel)

# others
library(lubridate)
```

### Convert txt corpus into a .csv 

```{r}
text <- "pressler_diary.txt"

# read in the doc's text line by line
readLines(text)

# examine the structure
str(readLines(text))
# we see this is a character vector with 11319 elements (or lines)

# paste() has a useful argument, collapse, which breaks the boundaries between
# elements, merging them into one!
text <- paste(readLines(text), collapse= " ")

text <- as.data.frame(text)

#c <- as.data.frame(c)

```

INSERT PREPARATORY STEPS
1. extract date from entries, and create a new row, date
2. number each row with an index number, if not already done
3. remember to create an exception for comments
4. assume that any row that doesn't have a date is the same date as the row above


```{r}

```





```{r}
clean_c <- text %>% 
  mutate(
      text = str_to_lower(text),
    # text = str_replace_all(text, "\n", " "), # replace '/n' carriage with " ". Probably unnecessary b/c of the past operation
      text = str_remove_all(text, "[:punct:]"), # remove punctuation
    ) %>% 
  rowwise()
```


```{r}
dtm_pressler <- DocumentTermMatrix(clean_c$text, 
                                   control = list(removePunctuation = TRUE,
                                   stopwords = FALSE))

dtm_pressler <- dtm_pressler %>% as.matrix()

dim(dtm_pressler)

most_frequent <- dtm_pressler %>% colSums()

most_frequent_df <- most_frequent %>% as.list() %>% as_tibble() %>%
  pivot_longer(everything())

most_frequent_df %>% arrange(desc(value))

most_frequent_df %>% arrange(desc(value)) %>% print(n = 20)
```



```{r}
most_frequent_df %>%
  mutate(label = ifelse(value > 1200, name, NA)) %>%
  ggplot() +
  geom_point(aes(reorder(name, -value),  value)) +
  geom_text_repel(aes(reorder(name, -value),  value, label = label),
                  max.overlaps = 20) +
  theme_tufte() +
  ylab("Frequency") +
  theme(
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    axis.ticks = element_blank()
  )
```


Zipf's Law (for many types of data studied in the physical and social sciences, the rank-frequency distribution is an inverse relation):

```{r}
most_frequent_df %>%
  arrange(desc(value)) %>%
  mutate(rank = 1:nrow(.)) %>%
  ggplot(aes(rank, value)) +
  geom_line() +
  ylab("Frequency") +
  xlab("Rank") +
  scale_x_log10() +
  scale_y_log10() +
  theme_tufte()

```

Similar results to the classroom Federalist Papers example. Let's remove stop words.


```{r}
dtm_pressler <- DocumentTermMatrix(clean_c$text, control = list(removePunctuation = TRUE, stopwords = stopwords("english")))
                                   
dtm_pressler <- dtm_pressler %>% as.matrix()

dim(dtm_pressler)

most_frequent <- dtm_pressler %>% colSums()

most_frequent_df <- most_frequent %>% as.list() %>% as_tibble() %>%
  pivot_longer(everything())

most_frequent_df %>% arrange(desc(value))
```

Run the 

```{r}
most_frequent_df %>%
  mutate(label = ifelse(value > 500, name, NA)) %>%
  ggplot() +
  geom_point(aes(reorder(name, -value),  value)) +
  geom_text_repel(aes(reorder(name, -value),  value, label = label),
                  max.overlaps = 20) +
  theme_tufte() +
  ylab("Frequency") +
  theme(
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    axis.ticks = element_blank()
  )

```


